### 2019-01-14 writing/thesis/chapters/methods.tex
Fix typo in surface integral term of corrector.
Some more work on results, mostly plots.
Plots will be added soon, are not final yet.

\sidetitle{Corrector}
The final step of the \aderdg{}-scheme is the corrector.
We multiply the system \cref{eq:conservation-law-gradient} by a space test function $\stestfunction$ and integrate over the space-time control volume.
This results, yet again, at the weak formulation of the \pde{}
\begin{equation}
  \label{eq:weak-pde}
\intdt{\intdcell{
\stestfunction[][v,n] \pdv{\Q}{t}
}}
+
\intdt{\intdcell{
    \stestfunction[][v,n] \left( \div{F(\Q, \gradQ } \right)
}}
=
\intdt{\intdcell{
    \stestfunction[][v,n] S(\Q, \bm{x}, t)
}}.
\end{equation}
We now insert our discrete approximations and apply the basis expansions \cref{eq:cell-approx-space,eq:cell-approx-space-time} to the space-time predictor.
The first part can be integrated by parts in time with the convenient result that only the boundary terms remain because the basis is constant in time.
We then integrate the flux divergence by parts in space and insert the Riemann solver to connect with the neighbouring elements.
Finally, we need to solve
\newcommand{\massMatrixDef}{\intdcell{
  \stestfunction[][v,n] \sbasis[][v,n']
}}
\begin{align}
\begin{split}
\label{eq:corrector}
\left(
\massMatrixDef
\right)
(\ssolCoeff[t^{n+1}][v,n'] - \ssolCoeff[t^n][v,n'])
&+
\left(\intdt{\intdcellb{
      \stestfunction[][v,n] \Riemann(\stpredictor[-], \gradient{\stpredictor[-]}; \stpredictor[+], \gradient{\stpredictor[+]}) \cdot \normal
}}\right)
-\\
\left(\intdt{\intdcell{
    \gradient{\stestfunction[][v,n]} \cdot  \stflux(\spredictor, \gradient{\spredictor})
}}\right)
&=
\left(\intdt{\intdcell{
      \stestfunction[][v,n] \stsource(\spredictor)
}}\right)
\end{split}
\end{align}
for the coefficients $\ssolCoeff[\nextTime][v,n]$ of the new solution.
Here the superscripts $\pm$ denotes values that are extrapolated to the boundaries.
Again, the computational effort can be vastly reduced by collecting the integrals into matrices and precomputing as much as possible.
The first term is the mass tensor with entries
\newcommand{\massMatrix}[1][]{\bm{M}_{#1}}
\begin{equation}
  \label{eq:mass-matrix}
  \massMatrix[v n n'] = \massMatrixDef = \volume \underbrace{\quadWeight[n] \delta_{n n'}}_{\text{diagonal}}
\end{equation}
which is, due to the orthogonal basis \pcref{eq:basis-orthogonality}, diagonal for each variable $v$ and thus trivial to invert.
We can then insert the definition of our basis function into our equation and arrive at
\begin{align}
  \massMatrix \left( \ssolCoeff[t+1] - \ssolCoeff[t] \right) &=
  \Delta t \left( \bm{a} - \bm{b} + \bm{s} \right) 
  \intertext{with}
a_{v,n} &= \sfluxCoeff[][n'] \intdcell{
  \sbasis[][v,n'] \gradient{\sbasis[][v,n]}(t)
}
\\
\label{eq:corrector-surface}
b_{v,n} &= \intdcellb{
    \stestfunction[][v,n] \Riemann \left( \spredictor[-], \gradient{\spredictor[-]}, \gradient{\spredictor[+]} \right) \cdot \normal
} \\
s_{v,n} &=
\ssourceCoeff[][v,n'] \intdcell{
  \sbasis[][v,n] \sbasis[][v,n']
}
,
\end{align}
where we evaluated the time-integrals by \cref{eq:integration-by-substitution}.
All quantities are now time-averaged~\pcref{eq:time-average} and are represented in the space basis~\pcref{eq:cell-approx-space}.
Note that we evaluate the Riemann problem for the time-averaged space-predictor.
This is justified by the linearity of our numerical flux~\cite{dumbser2008unified,dumbser2010arbitrary}.
The surface integral \pcref{eq:corrector-surface} can be evaluated by summing over the contributions of the faces of each cell, which are computed by integrating the extrapolated space predictor with Gaussian quadrature.
Finally, we can solve \cref{eq:corrector} for the new unknows $\ssolCoeff[k+1]$
\begin{align}\label{eq:update-predictor}
\begin{split}
  %\bm{u}^{n+1}
  \ssolCoeff[k+1][v]
  &= \ssolCoeff[k][v] + \Delta t (\operatorname{update}) \\
  \operatorname{update} &= \massMatrix[v]^{-1} \left( \bm{a}_v - \bm{b}_v + \bm{s}_v \right)
\end{split}
\end{align}
which is clearly of the form of a one-step scheme.

@@

A relatively recent way of dealing with this problem is the finite volume subcell limiter.
Our discussion follows the one in~\cite{dumbser2016simple}.
This limiting is an a posteriori limiting, which means that we first evaluate a timestep with an unlimited \aderdg{}-method and then check, whether our solution is \enquote{correct}.
In our case, we check whether the solution is a finite floating point number.
We also check whether it is physically admissible with the criterion\todo{Do I actually check for pos.\ of Z?}
\begin{equation}
  \label{eq:limiting-physical}
  \operatorname{is-admissible}(\Q) =
  \begin{cases}
    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZZ > 0 \\
    \text{false} & \text{otherwise}.
  \end{cases}
\end{equation}
The positivity of the pressure implies positivity of energy.
\todo{Mention dmp if I end up using it.}

If a solution violates our criterion, we recompute the last timestep for the offending cells with a limited finite volume method.
In our case we use the \muscl{}-method (\cref{sec:muscl}).
The recomputation starts by subdividing the infringing cell into $N_s = 2N + 1$ subcells.
This number of subcells has the advantage that we do not lose spatial resolution and that we can use the same timestep size for both cell types.
The reason for this is that the \textsc{cfl}-conditions for both schemes \pcref{eq:cfl-aderdg,eq:cfl-muscl} coincide for our choice of $N_s$.
\begin{figure}[htb]
  \centering
  \includegraphics[scale=0.7]{thesis_aderdg_subcell_grid}
  \caption{\label{fig:limiting-subcells}Conversion from \dg{}-dofs to fv-dofs. Image taken from~\cite{dumbser2018conformal}. }
\end{figure}
\todo{Cite source for subcells~\pcref{fig:limiting-subcells}. See guidebook. NOTE THAT IT IS MODIFIED. Also: Fix size, currently font is too small}

>>>>

\sidetitle{Corrector}
The final step of the \aderdg{}-scheme is the corrector.
We multiply the system \cref{eq:conservation-law-gradient} by a space test function $\stestfunction$ and integrate over the space-time control volume.
This results, yet again, at the weak formulation of the \pde{}
\begin{equation}
  \label{eq:weak-pde}
\intdt{\intdcell{
\stestfunction[][v,n] \pdv{\Q}{t}
}}
+
\intdt{\intdcell{
    \stestfunction[][v,n] \left( \div{F(\Q, \gradQ } \right)
}}
=
\intdt{\intdcell{
    \stestfunction[][v,n] S(\Q, \bm{x}, t)
}}.
\end{equation}
We now insert our discrete approximations and apply the basis expansions \cref{eq:cell-approx-space,eq:cell-approx-space-time} to the space-time predictor.
The first part can be integrated by parts in time with the convenient result that only the boundary terms remain because the basis is constant in time.
We then integrate the flux divergence by parts in space and insert the Riemann solver to connect with the neighbouring elements.
Finally, we need to solve
\newcommand{\massMatrixDef}{\intdcell{
  \stestfunction[][v,n] \sbasis[][v,n']
}}
\begin{align}
\begin{split}
\label{eq:corrector}
\left(
\massMatrixDef
\right)
(\ssolCoeff[t^{n+1}][v,n'] - \ssolCoeff[t^n][v,n'])
&+
\left(\intdt{\intdcellb{
      \stestfunction[][v,n] \Riemann(\stpredictor[-], \gradient{\stpredictor[-]}; \stpredictor[+], \gradient{\stpredictor[+]}) \cdot \normal
}}\right)
-\\
\left(\intdt{\intdcell{
    \gradient{\stestfunction[][v,n]} \cdot  \stflux(\spredictor, \gradient{\spredictor})
}}\right)
&=
\left(\intdt{\intdcell{
      \stestfunction[][v,n] \stsource(\spredictor)
}}\right)
\end{split}
\end{align}
for the coefficients $\ssolCoeff[\nextTime][v,n]$ of the new solution.
Here the superscripts $\pm$ denotes values that are extrapolated to the boundaries.
Again, the computational effort can be vastly reduced by collecting the integrals into matrices and precomputing as much as possible.
The first term is the mass tensor with entries
\newcommand{\massMatrix}[1][]{\bm{M}_{#1}}
\begin{equation}
  \label{eq:mass-matrix}
  \massMatrix[v n n'] = \massMatrixDef = \volume \underbrace{\quadWeight[n] \delta_{n n'}}_{\text{diagonal}}
\end{equation}
which is, due to the orthogonal basis \pcref{eq:basis-orthogonality}, diagonal for each variable $v$ and thus trivial to invert.
We can then insert the definition of our basis function into our equation and arrive at
\begin{align}
  \massMatrix \left( \ssolCoeff[t+1] - \ssolCoeff[t] \right) &=
  \Delta t \left( \bm{a} - \bm{b} + \bm{s} \right) 
  \intertext{with}
a_{v,n} &= \sfluxCoeff[][n'] \intdcell{
  \sbasis[][v,n'] \gradient{\sbasis[][v,n]}(t)
}
\\
\label{eq:corrector-surface}
b_{v,n} &= \intdcellb{
    \stestfunction[][v,n] \Riemann \left( \spredictor[-], \gradient{\spredictor[-]}; \spredictor[+], \gradient{\spredictor[+]} \right) \cdot \normal
} \\
s_{v,n} &=
\ssourceCoeff[][v,n'] \intdcell{
  \sbasis[][v,n] \sbasis[][v,n']
}
,
\end{align}
where we evaluated the time-integrals by \cref{eq:integration-by-substitution}.
All quantities are now time-averaged~\pcref{eq:time-average} and are represented in the space basis~\pcref{eq:cell-approx-space}.
Note that we evaluate the Riemann problem for the time-averaged space-predictor.
This is justified by the linearity of our numerical flux~\cite{dumbser2008unified,dumbser2010arbitrary}.
The surface integral \pcref{eq:corrector-surface} can be evaluated by summing over the contributions of the faces of each cell, which are computed by integrating the extrapolated space predictor with Gaussian quadrature.
Finally, we can solve \cref{eq:corrector} for the new unknows $\ssolCoeff[k+1]$
\begin{align}\label{eq:update-predictor}
\begin{split}
  %\bm{u}^{n+1}
  \ssolCoeff[k+1][v]
  &= \ssolCoeff[k][v] + \Delta t (\operatorname{update}) \\
  \operatorname{update} &= \massMatrix[v]^{-1} \left( \bm{a}_v - \bm{b}_v + \bm{s}_v \right)
\end{split}
\end{align}
which is clearly of the form of a one-step scheme.

@@

A relatively recent way of dealing with this problem is the finite volume subcell limiter.
Our discussion follows the one in~\cite{dumbser2016simple}.
This limiting is an a posteriori limiting, which means that we first evaluate a timestep with an unlimited \aderdg{}-method and then check, whether our solution is \enquote{correct}.
In our case, we check whether the solution is a finite floating point number.
We also check whether it is physically admissible with the criterion\todo{Do I actually check for pos.\ of Z?}
\begin{equation}
  \label{eq:limiting-physical}
  \operatorname{is-admissible}(\Q) =
  \begin{cases}
    \text{true} & \Qrho > 0 \land \pressure > 0 \land \QZZ > 0 \\
    \text{false} & \text{otherwise}.
  \end{cases}
\end{equation}
The positivity of the pressure implies positivity of energy.

\todo{Reread dmp description, fix formulas.}
To combat the Gibbs phenomenon, we can make use of the discrete maximum principle (\textsc{dmp}).
This criterion marks cells as troubled that have a numerical solution that is significantly higher or lower than the solutions of its neighbours.
\begin{align}
\min (u(y, t^{\curTime})) - \delta &\leq u^*(y, t^{\nextTime}) \leq \max (u(y, t^{\curTime})) + \delta
%
%
\intertext{with tolerance}
\delta &= \max \left(
  \varepsilon_0, \varepsilon \left(
         \max(u(y,t^{\curTime})) -
         \min(u(y,t^{\curTime}))
  \right)
  \right)
\end{align}
The parameters $\varepsilon$ and $\varepsilon_0$ can be set freely.
The former is controls by which factor the local jump can differ from its neighbourhood, the latter is needed for zero jumps~\cite{dumbser2016simple}.
Note that this criterion is suspectible for false positives, this is especially a problem in the presence of a source term.
\todo{Mention problems with source term?}

If a solution violates our criterion, we recompute the last timestep for the offending cells with a limited finite volume method.
In our case we use the \muscl{}-method (\cref{sec:muscl}).
The recomputation starts by subdividing the infringing cell into $N_s = 2N + 1$ subcells.
This number of subcells has the advantage that we do not lose spatial resolution and that we can use the same timestep size for both cell types.
The reason for this is that the \textsc{cfl}-conditions for both schemes \pcref{eq:cfl-aderdg,eq:cfl-muscl} coincide for our choice of $N_s$.
\begin{figure}[htb]
  \centering
  \includegraphics[scale=0.7]{thesis_aderdg_subcell_grid}
  \caption{\label{fig:limiting-subcells}Conversion from \dg{} degrees of freedoms to finite volume degree of freedoms. Image taken from~\cite{dumbser2018conformal}. }
\end{figure}
\todo{Cite source for subcells~\pcref{fig:limiting-subcells}. See guidebook. NOTE THAT IT IS MODIFIED. Also: Fix size, currently font is too small}

### 2019-01-14 writing/thesis/chapters/results.tex
Some more work on results, mostly plots.
Plots will be added soon, are not final yet.

\chapter{Results}\label{chap:results}
\section{Convergence Test}\label{sec:results-convergence}
\begin{table}[htb]
  \centering
\caption{Numerical order of convergence of ADER-DG method}%
\label{tab:convergence-order}
\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
\toprule
{Order} & {$L_1$} & {$L_2$} & {$L_\infty$}\\ \midrule
1 & 2.03 & 2.00 & 1.92\\
2 & 2.56 & 2.55 & 2.55\\
3 & 3.43 & 3.40 & 3.44\\
4 & 4.27 & 4.27 & 4.36\\
5 & 5.00 & 5.02 & 5.08\\
6 & 4.46 & 4.50 & 4.65\\
\bottomrule
\end{tabular}
\end{table}

@@

\newcommand{\error}{\operatorname{Total-Error}}

We first observe that for our approximation space $\broken$ we can split up the error as a sum over all cells
\begin{equation}
  \label{eq:lp-norm-broken}
 %\Vert f(\bm{x}) \Vert = \sum_{\cell[] \in \broken} \Vert f_{\cell[]} (\bm{x}) \Vert_p,
  \error(t,p) = \sum_{\cell[] \in \broken} \error_{\cell[]}(t,p)
\end{equation}
where $\error_{\cell[]}$ is the error in the cell $\cell[]$.

\todo{Describe how to integrate the error for cells, and effect of volume}
We evaluate the cell-wise error with Gaussian quadrature using \cref{eq:integration-by-substitution}
 \begin{equation}
   \Vert f_K(x) \Vert_p = \left( V \sum_{\bm{i}} \vert f(\bm{x}_i, t) - \hat{f}(\bm{x}_i, t) \vert^p w_{{\bm{i}}}  \right)^{1/p},
 \end{equation}
where $V = \Delta x \Delta y$ is the volume of each two-dimensional cell.
\todo{Use quadNodes, quadWeights and volume macro}
The sum runs over all quadrature nodes $x_i$ with weights $w_i$.
We use ten nodes for all orders and evaluate our solution for all nodes.
In this way we ensure a fair comparision.

For the limiting case of $p \to \infty$ we use the maximum point-wise error.

We compute the error for the manufactured-solution scenario (\cref{sec:manufactured-solution}).
Looking at the plot for the $L_2$ error (refer to plot here) shows that our method converges for all tested polynomial orders.
\todo{Preliminary results used here!}

To compute the numerical order of convergence, we perform a linear regression of the logarithm of the error vs.\ the logarithm of the meshsize.
The size of the slope is then the convergence order.
We can see (\cref{tab:convergence-order}) that our numerical convergence rate increases with the polynomial order.
We do not achieve the optimal theoretical order of convergence of $N+1$.
In~\cite{dumbser2010arbitrary}, which use a similar numerical method and the same scenario, but a different grid, \citeauthor{dumbser2010arbitrary} achieves the optimal order for most polynomial orders.
Some \textsc{dg}-methods of odd order only achieve a numerical convergence order of $N+\nicefrac{1}{2}$.

@@

\sidetitle{Taylor-Green Vortex}
We use an \aderdg{}-scheme of order 5 with a mesh of size $27 \times 27$ cells to simulate the Taylor-Green Vortex.
The simulation ran for \SI{10}{\s}.
Our solution results in the expected streamlines (figure xx).
Furthermore, we compare our results with the analytical solution for the incrompressible case.
We achieve a small error (figure xx) for both pressure and velocity.
The small errors are expected and not only stem from numerical inaccuracies but primarily from the fact that we simulate a compressible fluid.
Note that the error is small over the entire domain, and not only close to the boundary, where we impose the analytical solution.
Overall, we notice a very good agreement with the results of~\cite{dumbser2016high} and the analytical solution.

\sidetitle{ABC Flow}
We use an \aderdg{}-scheme of order 2 with a mesh consisting of $27 \times 27 \times 27$ cells to simulate the \textsc{abc}-flow.
We run the simulation for \SI{1}{\s}.
Figure xxx shows two slices of the simulation, figure xxx compares our numerical approximation of the pressure to the analytical solution.
Again, our solution agrees with the analytical solution.

\sidetitle{Lid-Driven Cavity}
We use a \muscl{}-limited \aderdg{}-scheme of order 3 with a mesh of size $27 \times 27$ for the Lid-Driven Cavity.
The streamlines agree with the expected solution but have two additional, smaller vortices in the bottom corners.
They do not appear in DUMBER but do appear in OTHERSOLUTION.
Additionally, we show a slice of the velocity in figure XXX, which also agrees with the solution of XXX.
Surprisingly, the limiter was not activated at all.
We noticed that we need the limiter when decreasing the speed of sound. 
The results for this scenario also agree with comparable reference solutions~\cite{ghia1982high}.

\section{Accurate Clouds}
\begin{itemize}
\item Cosine Bubble
\item Two Bubbles
\end{itemize}
Show bubbles, mention they look similar
\section{Time-to-solution: AMR vs Static Mesh}\label{sec:results-tts-amr}
To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
In detail, we compare
\begin{description}
\item[AMR] We use a coarse mesh with just $27 \times 27$ cells.
  Each cell can be refined up to three times.
  That is, the cells have sidelengths of roughly $\left(\SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
  As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
\item[Fine] We use a uniform grid where all cells have a sidelength corresponding to the finest mesh of the \amr{}-test case.
  In addition, we disable the reduction of global observables.
\end{description}
Note, that while our \amr{} criterion is able to cope with an additional, coarser level, the current implementation in \exahype{} is unstable for this scenario.
This is why we only report an \amr{} run with one level of dynamic refinement.

@@

>>>>

\chapter{Results}\label{chap:results}
We discussed various scenarios in the previous chapter.
In this chapter, we use them to gauge the quality of our numerical scheme.
We start with a convergence test, followed by two standard testing scenarios.
Next, we simulate two different cloud scenarios and check, whether our \amr{} criterion is useful.

\newcommand{\error}{\operatorname{Total-Error}}
\section{Convergence Test}\label{sec:results-convergence}
For the convergence test, we run our manufactured solution scenario~(\cref{sec:manufactured-solution}) for all orders 1 to 6 and for number of cells $3^2, 9^2, 27^2$ and $81^2 $.

We first observe that for our approximation space $\broken$ we can split up the error as a sum over all cells.
% \begin{equation}
%   \label{eq:lp-norm-broken}
%  %\Vert f(\bm{x}) \Vert = \sum_{\cell[] \in \broken} \Vert f_{\cell[]} (\bm{x}) \Vert_p,
%   \error(t,p) = \sum_{\cell[] \in \broken} \error_{\cell[]}(t,p)
% \end{equation}
% where $\error_{\cell[]}$ is the error in the cell $\cell[]$.
\todo{Describe how to integrate the error for cells, and effect of volume}
We evaluate the cell-wise error with Gaussian quadrature using \cref{eq:integration-by-substitution}
 \begin{equation}
%   \Vert f(\bm{x}, t) - \hat{f}(\bm{x}, t) \Vert_p^p =
   \error(t,p) = 
   \left( \sum_{\cell[i] \in \broken}
    \left( V \sum_{\bm{j}} \vert f^{\cell[i]}(\bm{x}_j, t) - \hat{f}^{\cell{i}}(\bm{x}_j, t) \vert^p w_{{\bm{j}}} \right) \right)^{1/p}.
 \end{equation}
Here, a superscript of $\cell[j]$ denotes the restriction of the function to a grid cell.
\todo{Use quad node macro here!}
To increase the quality of the error computation, we evaluate both analytical and approximate solution at the quadrature nodes of a scheme with 10 quadrature nodes $x_j$ with weights $w_j$.
We then use these nodes to compute the approximation error per cell.

For the limiting case of $p \to \infty$ we use the maximum point-wise error over all nodal points.

@@

\begin{table}[htb]
  \centering
\caption{Numerical order of convergence of ADER-DG method}%
\label{tab:convergence-order}
\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
\toprule
{Polynomial Order $N$} & {$L_1$} & {$L_2$} & {$L_\infty$}\\ \midrule
1 & 2.03 & 2.00 & 1.92\\
2 & 2.56 & 2.55 & 2.55\\
3 & 3.43 & 3.40 & 3.44\\
4 & 4.27 & 4.27 & 4.36\\
5 & 5.00 & 5.02 & 5.08\\
6 & 4.46 & 4.50 & 4.65\\
\bottomrule
\end{tabular}
\end{table}

To compute the numerical order of convergence, we perform a linear regression of the logarithm of the error vs.\ the logarithm of the meshsize.
The size of the slope is then the convergence order.
Looking at the plot for the $L_2$ error~(\cref{fig:convergence-l2-error}) shows that our method converges for all tested polynomial orders.
Note that the error for the finest grid with order 6 is worse than the error for order 5.
For all other meshsizes and orders, a higher order indicates a smaller error.
If we compare our errors with the optimal order of convergence, we notice that while order 1 exhibits the theoretical order of convergence of 2, larger polynomial orders lead to diminishing returns.

The same is true for other error norms (\cref{tab:convergence-order}).
This means, that we in general do not achieve the optimal theoretical order of convergence.
In~\cite{dumbser2010arbitrary}, which use a similar numerical method and the same scenario, but a different grid, \citeauthor{dumbser2010arbitrary} achieves the optimal order for most polynomial orders.
Some \textsc{dg}-methods of odd order only achieve a numerical convergence order of $N+\nicefrac{1}{2}$.

@@

\sidetitle{Taylor-Green Vortex}
We use an \aderdg{}-scheme of order 5 with a mesh of size $27 \times 27$ cells to simulate the Taylor-Green Vortex.
The simulation ran for \SI{10}{\s}.
Our solution results in the expected streamlines (\cref{fig:taylor-green-streamlines}).
Furthermore, we compare our results with the analytical solution for the incrompressible case.
We achieve a small error~(\cref{fig:taylor-green-result}) for both pressure and velocity.
The small errors are expected and not only stem from numerical inaccuracies but primarily from the fact that we simulate a compressible fluid.
Note that the error is small over the entire domain, and not only close to the boundary, where we impose the analytical solution.
Overall, we notice a very good agreement with both the results of~\cite{dumbser2016high} and the analytical solution.

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.5\textwidth]{thesis_taylor_green_stream}
  \caption{Streamlines for Taylor-Green vortex}
  \label{fig:taylor-green-streamlines}
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{thesis_taylor_green_vel}
    \caption{Position vs.\ velocity}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{thesis_taylor_green_pressure}
    \caption{Position vs.\ pressure}
  \end{subfigure}
  \caption{\label{fig:taylor-green-result}%
    Comparison of Taylor-Green simulation with analytical solution.
    The former is represented by the scatter plot, the latter by the gray line.
    Note that we only show every 5th point.}
\end{figure}

\sidetitle{ABC Flow}
We use an \aderdg{}-scheme of order 2 with a mesh consisting of $27 \times 27 \times 27$ cells to simulate the \textsc{abc}-flow.
We run the simulation for \SI{1}{\s}.
Figure xxx shows two slices of the simulation, figure xxx compares our numerical approximation of the pressure to the analytical solution.
Again, our solution agrees with the analytical solution.
\todo{Velocity?}

\sidetitle{Lid-Driven Cavity}
\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=1.2\textwidth]{thesis_lid_driven_cavity_stream}
    \caption{\label{fig:lid-driven-cavity-streamlines}%
      Streamlines of the cavity flow.}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.7\textwidth}
    \centering
    \includegraphics{thesis_lid_driven_cavity}
    \caption{\label{fig:lid-driven-cavity-result}%
      Plot of velocity slices. Lines are our soulution, scatter plot shows reference solution~\cite{ghia1982high}.}
  \end{subfigure}

  \caption{Lid-Driven Cavity solution at $t=\SI{30}{\s}$}
  \label{fig:lid-driven-cavity}
\end{figure}

We use a \muscl{}-limited \aderdg{}-scheme of order 3 with a mesh of size $27 \times 27$ for the Lid-Driven Cavity.
The streamlines~(\cref{fig:lid-driven-cavity-streamlines}) agree with the expected solution but have two additional, smaller vortices in the bottom corners.
They do not appear in~\cite{dumbser2010arbitrary} but do appear in~\cite{ghia1982high}.
Additionally, we show the velocity along both axes in \cref{fig:lid-driven-cavity-result}.
They too agree with the reference solution of~\cite{ghia1982high}.

Surprisingly, the limiter was not activated at all.
We noticed that we need the limiter when decreasing the speed of sound.

\section{Accurate Clouds}
\begin{itemize}
\item Cosine Bubble
\item Two Bubbles
\end{itemize}
The cosine bubble scenario$\ldots$

\sidetitle{Two Bubbles}
We ran the second scenario with the same \amr{} settings as the first one.
The results in (\cref{fig:results-two-bubbles}) are comparable to the reference solution~\cite{muller2010adaptive} for the first seven minutes\todo{Recreate contour plots with amr version!}.
Note that the final plot at \SI{7}{\min} looks different in our simulation.
A possible source for this is that we use a different equation set than~\cite{muller2010adaptive}.
While we use a general purpose set with small modifications for atmospheric flows, they use a equation set that is fully focussed on this scenario.
Furthermore, we use the full Navier-Stokes viscous fluxes instead of an approximation.

\begin{figure}[p]
  \vspace*{-4.5cm}
  \thisfloatpagestyle{empty}
  \centering
  \begin{subfigure}{1\textwidth}
    \centering
    \includegraphics{thesis_two_bubbles_contour_collage.pdf}
  \end{subfigure}
  % \begin{subfigure}[t]{0.5\textwidth}
  %   \centering
  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t0}
  % \end{subfigure}~%
  % \begin{subfigure}[t]{0.5\textwidth}
  %   \centering
  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t240}
  % \end{subfigure}
  % \begin{subfigure}[t]{0.5\textwidth}
  %   \centering
  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t420}
  % \end{subfigure}~%
  % \begin{subfigure}[t]{0.5\textwidth}
  %   \centering
  %   \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.8cm, clip]{thesis_two_bubbles_contour_t600}
  % \end{subfigure}
  \vspace*{1cm}
  \begin{subfigure}[t]{1\textwidth}
    \centering
    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm, clip, scale=1.2]{giraldo_results_two_bubbles}
  \end{subfigure}
  \caption{\label{fig:results-two-bubbles}%
    Results for two bubble scenario.
    On the top is our, the bottom plots are taken from~\cite{muller2010adaptive}.
  Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.
}
\end{figure}

\section{Time-to-solution: AMR vs Static Mesh}\label{sec:results-tts-amr}
To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
In detail, we compare
\begin{description}
\item[AMR] We use a coarse mesh with just $27 \times 27$ cells.
  Each cell can be refined up to three times.
  That is, the cells have sidelengths of roughly $\left(\SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
  As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
\item[Fine] We use a uniform grid where all cells have a sidelength corresponding to the finest mesh of the \amr{}-test case.
  In addition, we disable the reduction of global observables.
\end{description}
Note, that while our \amr{} criterion is able to cope with an additional, coarser level, the current implementation in \exahype{} is unstable for this scenario.
This is why we only report an \amr{} run with one level of dynamic refinement.

@@

\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics{thesis_detonation_euler_nodmp_pressure}
    \caption{Pressure, Euler, no \textsc{dmp}}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics{thesis_detonation_euler_dmp_pressure}
    \caption{Pressure, Euler, \textsc{dmp}}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics{thesis_detonation_ns_pressure}
    \caption{Pressure, \textsc{NS}, no \textsc{dmp}}
  \end{subfigure}

  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics{thesis_detonation_euler_nodmp_Z}
    \caption{$Z$, Euler, no \textsc{dmp}}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics{thesis_detonation_euler_dmp_Z}
    \caption{$Z$, Euler, \textsc{dmp}}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics{thesis_detonation_ns_Z}
    \caption{$Z$, \textsc{NS}, no \textsc{dmp}}
  \end{subfigure}

  \caption{\label{fig:detonation-line-plots}%
    Slices along the $x$-axis for our three configurations.
    We only show one half of the slice because the scenario is symmetric.
  }
\end{figure}
